Dynamic Prediction of Non-Guassian Outcome with fast Generalized Functional Principal Analysis

### 2023-03-16 Write-ups/Manuscript.Rmd
simulation of GLMM adaptvie

@@

>>>>

colMeans(ise_mat)
```

```{r, eval=FALSE}
# calculate ISE on binned grid
ise_ref_mat <- matrix(NA, nrow = M, ncol = 4) # row index iteration, col index max observation time
colnames(ise_ref_mat) <- c("t200", "t400", "t600", "t800")

for(m in 1:M){
  # true value at midpoints
  pred_eta <- pred_lst_ref[[m]]

  ise_ref_mat[m, ] <- ise_m
}

colMeans(ise_ref_mat)
```

@@

colMeans(auc_mat)
```

```{r, eval=FALSE}
# calculate AUC on unbinned grid
auc_mat_ref <- matrix(NA, nrow = M, ncol = 4) # row index iteration, col index max observation time
colnames(auc_mat_ref) <- c("t200", "t400", "t600", "t800")

for(m in 1:M){
  # true value as matrix
  Y_mat <- sim_data[[m]]  %>% select(id, sind_inx, Y) %>% 
    pivot_wider(names_from = id, values_from = Y) %>%
    column_to_rownames("sind_inx")

    t <- t_vec[i]
    # predicted value
    pred_name <- paste("pred_t", t, sep = "")
    pred_mat <- pred_lst_ref[[m]] %>% select(id, sind, all_of(pred_name)) %>% 
      pivot_wider(names_from = id, values_from = all_of(pred_name)) %>%
      column_to_rownames("sind")
    pred_mat <- exp(pred_mat)/(1+exp(pred_mat))
    row_id <- complete.cases(pred_mat)

    # calculate AUC, skip subjects with no variation in outcome Y
    auc_lst <- lapply(1:N, function(x){
      auc_try <- try(performance(prediction(pred_mat[row_id, x], Y_mat[row_id, x]), "auc"), 
                     silent = T)
      auc_pref <- ifelse(class(auc_try)=="try-error",NA, auc_try@y.values)
      return(auc_pref)               
    })
